---
title: CV
name: Dongho (Tom)
surname: Choi
position: "PhD Student"
address: "263 Louise Pound Hall"
phone: +1 (420) 875-3918 
email: "tom.choi@huskers.unl.edu"
github: tomchoi91
linkedin: dongho-choi-b44801133/
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "Dongho (Tom) is a Doctoral student in University of Nebraska-Lincoln majoring in Psychological Studies in Education."
output: 
  vitae::markdowncv:
    theme: kjhealy
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

## Some stuff about me

 * I am an international student from South Korea.
 * I like 90s movies.
 * I like watching streamers playing games which I never played.
 
## Skills

 * I can speak Korean (native) and English (fleunt).
 * I am proficient in SPSS, SAS, R, and Mplus.
 * I know how to use SQL.

## Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "PhD student, Educational Psychology", "2018-Present", "University of Nebraska-Lincoln", "Lincoln, USA",
  "BA, Counseling Psychology", "2017", "Handong Global University", "Pohang, South Korea",
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

## Publications

```{r}
library(dplyr)
bibliography_entries("pub1.bib") %>%
  arrange(desc(author$family),issued)


```

## Manuscripts under review or in press

```{r}
library(dplyr)

bibliography_entries("inprogress.bib") %>%
  arrange(desc(author$family), issued)
```

## Presentations

```{r}
library(dplyr)

bibliography_entries("presentation.bib") %>%
  arrange(desc(issued))
```


## Research experiences

```{r}
tribble(
  ~ Period, ~ Position, ~ Institution, ~ Responsibility,
  "Sep.2018 ~ present", "Graduate Research Assistant", "Nebraska Center for Research on Children, Youth, Families & Schools, University of Nebraska–Lincoln","Data analysis",
  "Nov.2017 ~ Feb.2018", "Undergraduate Research Assistant", "The Effect of Probiotics on Human Cognitive Function and Emotional Stability, Principal investigator: Sung-Man Shin Ph.D.", "Data analysis",
  "Feb.2016 ~ Dec.2017", "Undergraduate Research Assistant", "Alcohol Abuse Status and Its Related Factors of Korean Rehabilitation Protection Recipients, Principal investigator: Young-Ok Han, Ph.D.", "Literature review, research design, production and distribution of the survey, data analysis, and writing manuscript",
  "Oct.2015 ~ Dec.2015", "Undergraduate Research Assistant", "Descriptive Research on First Generation Students – In Comparison with Second Generation Students in ROK (South Korea), Principal investigator: Sung-Man Shin Ph.D.", "Literature review, research design, production and distribution of the survey, and data analysis",
  "Jun.2015 ~ Mar.2016", "Undergraduate Research Assistant", "Exploratory Research on Identity Formation Courses in Christian Higher Education Institutes in South Korea and the United States, Principal investigator: Nicholas Lantinga, Ph.D.", "Data collection"
) %>% 
  detailed_entries(
    Institution,
    Period, 
    Responsibility,
    Position
  )

```

## Teaching experiences

```{r}
tribble(
  ~ Period, ~ Position, ~ Institution, ~ Responsibility,
  "Mar.2017 ~ Jun.2017", "Teaching Assistant", "‘Abnormal Psychology’, a counseling psychology major course","Organizing a field trip, grading, and checking attendance",
  "Mar.2016 ~ Jun.2016", "Teaching Assistant", "‘The Handong Character Build-up’, a freshman mandatory course", "Grading and checking attendance"
) %>% 
  detailed_entries(
    Institution,
    Period, 
    Responsibility,
    Position
  )

```

## Awards and honors

```{r}
library(tibble)
tribble(
  ~ Year, ~ Award, ~ Institution,
  "2018", "Othmer Fellowship", "University of Nebraska-Lincoln",
  "2017", "Second Placing at Student‐First‐Authored Poster Contest","APA",
  "2016", "Excellence award on Gambling Addiction Prevention Student Activity", "Korea Center on Gambling Problems",
  "2015", "First placing at Undergraduate Student research contest", "Handong Global University",
  "2014", "Academic Excellence Scholarship from the university", "Handong Global University"
) %>% 
  brief_entries(Award, Year, Institution)
```
