
\nocite{*}
% \printbibliography[title=Publications]

% Can instead manually enter publications as shown:
\section{Conference Proceedings}
\orderedouterlist{

% \entry{S. Petridis, J. Shen, \textbf{D. Cetin} and M. Pantic, "Visual-Only Recognition of Normal, Whispered And Silent Speech", \textit{IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP), April 2018}}
\entry{Cunha, A. B., Babik, I., \textbf{Choi, D.}, Koziol, N., Harbourne, R., Dusing, S., McCoy, S., Bovaird, J., \& Lobo, M. (2021, April). Performance after mastery of means-end problem solving differs in children with mild versus significant motor delays. \textit{Poster presented at the Society for Research in Child Development Biennial Meeting, Virtual.}}

\entry{Babik, I., Cunha, A. B., \textbf{Choi, D.}, Koziol, N., Harbourne, R., Dusing, S. C., McCoy, S. W., Bovaird, J., \& Lobo, M. A. (2021, February). START-Play intervention advanced reaching outcomes in children with significant but not mild motor delay. \textit{Paper presented to the Combined Sections Meeting of the American Physical Therapy Association, Virtual.}}

\entry{Shin, S., \textbf{Choi, D.}, Park, K., \& Song, Y. (2018, August). Examining Trajectory in Children’s Mobile Phone Dependency Using Latent Growth Modeling Analysis. \textit{Poster presented at 2018 American Psychological Association Annual Convention. San Francisco, CA.}}

\entry{Koo, K., \textbf{Choi, D.}, \& Song, Y. (2018, August). Am I welcomed here? Campus climate and psychological well-being among international college students. \textit{Poster presented at 2018 American Psychological Association Annual Convention. San Francisco, CA.}}

\entry{Shin, S., Song, Y., \textbf{Choi, D.}, \& Lee, M. (2017). Relation Between Drinking and Psychological Variables of Korean Rehabilitation Protection Recipients. \textit{Poster presented at 2017 American Psychological Association(APA) Annual Convention, Washington, D.C.}}

\entry{Lee, Y., \textbf{Choi, D.}, Koo., K, \& Choi, J. (2017). Discrepancy between Reality and Expectation: Pathway to  Smartphone Dependency among Adolescents in Korea. \textit{Poster presented at 2017 American Psychological Association(APA) Annual Convention, Washington, D.C.}}

\entry{Shin, S., Park Y., Choi. Y., Jung. J., \& \textbf{Choi, D.} (2016). The Mediating Effect of Attention on the Relationship between Smartphone Dependency and Aggression. \textit{Poster presented at 2016 Korean Psychological Association (KPA) Conference, Gunsan.}}

\entry{Cho, Y., \textbf{Choi, D.}, Kim, D., Kim, J., \& Lee, Y. (2016). The Relationship between Attachment Anxiety and College Adaptation: The Mediating Effect of Smartphone Addiction and Existential Spiritual Well-being. \textit{Poster presented at 2016 Korean Clinical Psychology Association (KCPA) Spring Conference, Chuncheon.}}
}
